--- 
title: "Antimicrobial Resistance Data Analysis with R"
author: "Matthijs Berends"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This book explains common methodologies for performing antimicrobial resistance (AMR) data analysis with R, using the `AMR` package."
---

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), "bookdown", "knitr", "rmarkdown", "AMR"
), "packages.bib")
```

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.
